\chapter{Introduction}
Magnetic Resonance is used to find energies of possible quantum transitions in materials.
A sample in an oscillating field can absorb energy when the oscillating frequency coincides with the energy difference between two quantum states. %and some other rules are met (include?)
In both experiments, an external magnetic field is applied to lift the degeneracy of different magnetic states of particles that carry a magnetic dipole, creating the different energy states.

\section{Zeeman Effect}
The \textsc{Zeeman} effect describes the splitting of a spectral line due to an external static magnetic field and is important in applications such as \textbf{ESR} and \textbf{NMR}, which will be discussed later on.

\subsection{Normal Zeeman Effect}
The effect that appears for spectral lines resulting from a transition between singlet states is called the \textbf{normal} effect.
For singlet states, the total angular momentum $\vec{J}$ is given solely by the angular momentum $\vec{L}$, which couples with the external magnetic field.

The change in energy is a function of this external field
\begin{equation*}
	\Delta E = -\mu_\text{z}\cdot B=m_l\mu_\text{B}B, \tag{$\vec{B}=B\hat{e}_\text{z}$}
\end{equation*}
where $\mu_\text{z}=-m_l\mu_\text{B}$ denotes the magnetic moment with the Bohr magneton $\mu_\text{B}=\frac{e\hbar}{2m_\text{e}}$.
Since there are $2l+1$ possible values for $m_l$, the energy levels split into $2l+1$ energy levels.
The selection rule $\Delta m_l=\pm 1$ reduces the number of possible lines.
For example, a transition between $l=2$ to $l=1$ states will result into nine lines.
However, as a consequence of the uniformity of the level splittings, only three different lines, each corresponding to the $\Delta m_l=-1,0,1$ transitions, are visible in the spectrum.

\subsection{Anomalous Zeeman Effect}
This effect appears for states with a nonzero total spin.
Consider an atom with the total spin $\vec{S}$ and orbital angular momentum $\vec{L}$.
We can then switch to a new basis $\ket{J, m_j}$ with $J=L+S$, whereas the total magnetic moment is given by
\begin{align*}
	\vec{\mu}_\text{tot} &= -\mu_\text{B}\left(g_\text{l}\frac{\vec{L}}{\hbar} + g_\text{s}\frac{\vec{S}}{\hbar}\right) \\
	&= -g_\text{J}\mu_\text{B}\frac{\vec{J}}{\hbar},
\end{align*}
where $g_\text{l}\approx 1$ and $g_\text{s}\approx 2$ are called the \textsc{Landé} factors.
By performing the vector addition of $\vec{L}$ and $\vec{S}$, $g_\text{J}$ takes the form
\begin{equation*}
	g_\text{j} = 1+\frac{J(J+1)+S(S+1)-L(L+1)}{2J(J+1)}.
\end{equation*}
Consider a doublet level transistion $\ce{^{2}P}_{1/2}\rightarrow \ce{^{2}S}_{1/2}$.
The selection rule $\Delta m_J =0, \pm 1$ gives 4 lines.

\section{ESR}

\section{NMR}
Nuclear Magnetic Resonance is used to analyze the different energy states that nuclei with a nonzero magnetic moment take in an external magnetic field.
NMR is used in medicine (MRI) or to detect isotopes of elements.
The resonance frequency is also affected by the electron hull of the atom (''nuclear shielding''), which makes it possible to analyze chemical structures with NMR.
Only nuclei that don't have an even number of protons and neutrons each can be analyzed, as protons and neutrons each form pairs that have opposing spin and thus have no net spin and magnetic moment.\\
In this experiment hydrogen atoms of different chemical compounds are analyzed.

\subsection{Resonance Frequency}

The energy of a hydrogen atom's proton's magnetic diopole $\mu_z = m \gamma \hbar$ in a magnetic field $B_0$ is
\begin{equation*}
	E = - \mu_z \cdot B_0 = m \gamma \hbar \cdot B_0,
\end{equation*}
where $m = \pm \tfrac{1}{2}$ denotes the magnetic quantum number and $\gamma$ the proton's gyromagnetic ratio.
The resulting resonance frequency is
\begin{equation*}
	f_0 = \frac{\Delta E}{h} = \frac{1}{2 \uppi} \gamma \cdot B_0,
\end{equation*}
which is \SI{60}{\mega\hertz} for the used field strength of \SI{1.41}{\tesla}.

\subsection{Nuclear Shielding}
A nucleus' environment can weaken the effective magnetic field that reaches the nucleus.
The resulting change in resonance frequency can be detected:
\begin{alignat*}{1}
	B_\text{eff} &= \left(1 - \sigma \right) \, B_0\\
	f_\text{r} &= \left(1 - \sigma \right) \, f_0
\end{alignat*}

\subsection{$\updelta$ Scale}
The exact resonance frequency is linearly dependent on the strength of the external magnetic field.
Calibrating this magnetic field to the required accuracies of $< \SI{1}{ppm}$ and accounting for temperature coefficients and drift is difficult at best.
Since only hydrogen atoms are analyzed and the expected resonance frequencies are very similar, frequencies are measured relative to the resoance frequency of the hydrogen atoms in a known chemical structure.

Tetramethylsilane proves to be a good reference compound, as it contains twelve hydrogens atoms which are chemically identical.

Frequencies are converted to the delta scale as
\begin{equation*}
	\delta = \frac{f - f_\text{TMS}}{f_\text{TMS}},
\end{equation*}
which is not dependent on $B_0$.
Values for delta are usually expressed in \si{ppm}.

\subsection{Spin-Spin Coupling}
The dipole moments of neighbouring nuclei can contribute to the external magnetic field.
Depending on the number of neighbouring atoms, this results in doublets, triplets or quaduplets instead of single peaks.
The frequency difference between peaks is independent of the external field, so it is specified directly.

For $n$ neighbouring, chemically equivalent nuclei $n + 1$ peaks are detected, with intensities proportional to ${{n + 1}\choose{m}}, m = 0 \dots n$.

Nuclei that are not chemically identical will result in more compliacated patterns.
