% !TEX root = ../05-Lattice-Vibration.tex
\chapter{Procedure}
\section{Model}
\todo{Please reword. Repetitive use of 'the'.}
The model consists of twelve thingmajigs and thirteen springs.
The first spring is connected to a stepper motor that can creates reciprocal harmonic motion at a selectable frequency and presents a fixed end to the chain.
The last spring is fixed to the end of the rail.

The thingmajigs consist of a piece of angle aluminium and have a threaded hole to mount additional weights.
Each thingmajig has a stripe of retroreflective material glued to its side.\todo{The word its means 'belonging to it'. It is a possessive pronoun like 'his'.}
They ride on a linear air bearing, which is a square tube sealed on both ends oriented on one of its edges.\todo{Relative clauses which give extra information must be separated off by commas.}
A turbine sends an air stream into the tube.
The tube's two sides facing upwards have a series of small holes to create an air cushion between the tube and the thingmajigs.
To dampen the oscillation after an experiment, the turbine's air inlet is blocked briefly.

\section{Data Acquisition}\label{sec:data_acq}
A camera with a horizontal linear CCD is used to capture the position the retroreflective stripes on the fifth and sixth thingmajig.
Prior to the experiment, the camera is aligned so the retroreflectors are in the plane of the CCD.\todo{When words which "set the scene" for the main part of the sentence appear at the front of the sentence, it is usual to offset them with a comma.}
A \texttt{LabView} program is used to read the two positions from the camera.
The program is then used to apply a fast fourier transform to the positions to find the frequencies of the individual modes and later to measure the amplitudes of single modes.
